Markdown file for Practical Machine Learning project.
=====================================================


Load data
---------
```{r}
library(caret)
```
* Load csv file.
```{r}
data<-read.csv("pml-training.csv")
```
Clean and partition data
-----------------------
* Remove rows which has new_window value yes.
```{r}
data<-data[data$new_window=="no",]
```
* Remove columns which has all NA values
```{r}
data<-data[,colSums(is.na(data)) != nrow(data)]
```
* Remove columns which has all empty values
```{r}
data<-data[,colSums(data=="") != nrow(data)]
```
* Remove first seven columns, as these values cannot be used for prediction.
```{r}
data<-data[,-c(1:7)]
```
* Partition data into training and cross validation set.
```{r}
inTrain <- createDataPartition(y=data$classe,p=0.75, list=FALSE)
training<-data[inTrain,]
cv<-data[-inTrain,]
```
Use machine learning
--------------------
* Create a trainControl for faster running to train function.
```{r}
trControl = trainControl(method = "cv", number = 4, allowParallel = TRUE,verboseIter = TRUE)
```
* Train using random forrest method.
```{r}
modFit <- train(classe ~., data=training, method="rf", prox=TRUE, trControl=trControl)
```
Corss validation
----------------
* Find acuracy of the model on cross validation set.
```{r}
pred <- predict(modFit,cv)
cv$predRight <- pred==cv$classe
tab<-table(pred,cv$classe)

```
* Find out the accuracy in percent.
```{r}
correct=0; wrong=0;
for(i in 1:5) { for(j in 1:5) { if(i==j) {correct=correct+tab[i,j]; } else {wrong=wrong+tab[i,j];} } }
percent<-100*(correct)/(correct+wrong)
```
*Accuracy of the used model

```{r}
print(percent)	
```
* If accuracy is good then use the model for predction on the actual test set.
```{r}
test_data<-read.csv("pml-testing.csv")
pred <- predict(modFit,test_data)
```
Prediction 
----------
```{r}
print(pred)
```
